%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Co-Curricular Experiences}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {TRAINER}
    {Competitive Programming Workshop}
    {UiTM Arau, Perlis}
    {2015-2017}
    {
      \begin{cvitems}
        \item {Conducted multiple workshops focusing on basic and advanced skills of competitive programming.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {TECHNICAL ASSISTANT}
    {Dota2 Tournament}
    {UiTM Arau, Perlis}
    {Sept. 2016}
    {
      \begin{cvitems}
        \item {Network setup and care for the well being of technical equipments.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {TRAINER}
    {Capture-the-Flag Workshop}
    {UiTM Shah Alam, Selangor}
    {2018}
    {
      \begin{cvitems}
        \item {Conducted multiple workshops which are focusing on introduction to security and capture-the-flag competition.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {PROGRAM MANAGER AND TRAINER}
    {Python and Data Science Workshop}
    {UiTM Shah Alam, Selangor}
    {2017-2018}
    {
      \begin{cvitems}
        \item {Conducted multiple workshops for every semesters which teach students about Python and Data Science skills.}
        \item {Introduction to Python programming languages.}
        \item {Introduction to Data Science and Machine Learning using available public Python packages.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {PROGRAM MANAGER}
    {Prosolve - Internal Programming Competition}
    {UiTM Shah Alam, Selangor}
    {2017-2018}
    {
      \begin{cvitems}
        \item {Ran a series of programming competition for every semesters.}
        \item {Using available open-source technologies such as Domjudge and Linux for the competition equipments.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
